Variants of G\"{o}del's Ontological Proof \\ in a Natural Deduction Calculus

### 2016-11-04 Papers/InProgress/NaturalDeduction/GodProof-ND.tex
Author names added
Bibliography edited

\author{Annika Siders \and Bruno Woltzenlogel Paleo}

\authorrunning{A.\~Siders \and B.\~Woltzenlogel Paleo}

\institute{ 
 Annika Siders \at 
  Department of Philosophy \\
  University of Helsinki\\
  P.O. Box 24 (Unioninkatu 40 A) \\
  Finland \\ 
  \email{annika.siders@helsinki.fi} \\
  +358 2941 29241[2em]
  \and 
  Bruno Woltzenlogel Paleo \at 
  Theory and Logic Group \\ 
  Vienna University of Technology \\ 
  Austria \\
   \email{bruno@logic.at} \\
  \and
    Bruno Woltzenlogel Paleo \at 
  Logic and Computation Group \\
  College of Engineering and Computer Science \\
  Australian National University \\
  Australia
    \email{bruno.woltzenlogel.paleo@anu.edu.au} 
}

@@

%\title{A Variant of G\"{o}del's Ontological Proof \\ in a Natural Deduction Calculus}
\author{}
\authorrunning{}
\institute{}
\maketitle

@@

\bibitem[{\itshape Bentert \& Benzm\"uller \& Streit \& Woltzenlogel Paleo(2016)}]{LeibnizOntologicalProof}
Bentert, M. \& Benzm\"uller, C. \& Streit, D. \& Woltzenlogel Paleo, B. 2016. {\itshape Analysis of an Ontological Proof Proposed by Leibniz}. [to appear in]  Death and Anti-Death, Volume 14: Four Decades after Michael Polanyi, Three Centuries after G. W. Leibniz. ed. Tandy, C. Ria University Press.

@@

\bibitem[{\itshape Benzm\"uller \& Weber \& Woltzenlogel Paleo(2015)}]{WorldCongressLogicAndReligion}
Benzm\"uller, C. \& Weber, L. \& Woltzenlogel Paleo, B. 2015. {\itshape Computer-Assisted Analysis of the Anderson-Hajek Ontological Controversy}. 1st World Congress on Logic and Religion.

@@

\bibitem[{\itshape Benzm\"uller \& Woltzenlogel Paleo(2013a)}]{IWIL}
Benzm\"uller, C. \& Woltzenlogel Paleo, B. 2013a. {\itshape G{\"{o}}del's God on the Computer}. 10th International Workshop on the Implementation of Logics. pp. 1--2.

@@

\bibitem[{\itshape Benzm\"uller \& Woltzenlogel Paleo(2014a)}]{WADT}
Benzm\"uller, C. \& Woltzenlogel Paleo, B. 2014a. {\itshape On Logic Embeddings and G\"odel's God}. Recent Trends in Algebraic Development Techniques.

\bibitem[{\itshape Benzm\"uller \& Woltzenlogel Paleo(2014b)}]{WADTPreProceedings}
Benzm\"uller, C. \& Woltzenlogel Paleo, B. 2014b. {\itshape On Logic Embeddings and G\"odel's God}. 22nd International Workshop on Algebraic Development Techniques, pp. 8--9.

\bibitem[{\itshape Benzm\"uller \& Woltzenlogel Paleo(2014c)}]{SquareOfOpposition}
Benzm\"uller, C. \& Woltzenlogel Paleo, B. 2014c. {\itshape Formalization and Automated Verification of G\"odel's Proof of God's Existence}. 4th World Congress on the Square of Opposition, pp. 24--25.

\bibitem[{\itshape Benzm\"uller \& Woltzenlogel Paleo(2014d)}]{ECAI2014}
Benzm\"uller, C. \& Woltzenlogel Paleo, B. 2014d. {\itshape Automating G{\"{o}}del's Ontological Proof of God's Existence with Higher-order Automated Theorem Provers}. ECAI 2014 - 21st European Conference on Artificial Intelligence, 18-22 August 2014, Prague, Czech Republic - Including Prestigious Applications of Intelligent Systems (PAIS 2014), pp. 93--98.

\bibitem[{\itshape Benzm\"uller \& Woltzenlogel Paleo(2015a)}]{CSRModalLogicInCoq}
Benzm\"uller, C. \& Woltzenlogel Paleo, B. 2015a. {\itshape Interacting with Modal Logics in the Coq Proof Assistant}. Computer Science - Theory and Applications - 10th International Computer Science Symposium in Russia, {CSR} 2015, Listvyanka, Russia, July   13-17, 2015, Proceedings. pp. 398--411.

\bibitem[{\itshape Benzm\"uller \& Woltzenlogel Paleo(2015b)}]{ReasoningWebSummerSchool}
Benzm\"uller, C. \& Woltzenlogel Paleo, B. 2015b. {\itshape Higher-Order Modal Logics: Automation and Applications}. Reasoning Web. Web Logic Rules - 11th International Summer School 2015, Berlin, Germany, July 31 - August 4, 2015, Tutorial Lectures. pp. 32--74.

\bibitem[{\itshape Benzm\"uller \& Woltzenlogel Paleo(2015c)}]{SpiritualQuest}
Benzm\"uller, C. \& Woltzenlogel Paleo, B. 2015c. {\itshape Experiments in Computational Metaphysics: G\"odel's Proof of God's Existence}. Science and Spiritual Quest: Proceedings of the 9th All India Students' Conference on Science and Spiritual Quest (IIT Kharagpur, 30th October -- 1st November). vol. 9. pp. 23--40.

\bibitem[{\itshape Benzm\"uller \& Woltzenlogel Paleo(2016a)}]{IJCAI2016}
Benzm\"uller, C. \& Woltzenlogel Paleo, B. 2016a. {\itshape The Inconsistency in G\"odel's Ontological Argument: A Success Story for AI in Metaphysics}. International Joint Conference on Artificial Intelligence - IJCAI.

\bibitem[{\itshape Benzm\"uller \& Woltzenlogel Paleo(2016b)}]{ModalCollapse}
Benzm\"uller, C. \& Woltzenlogel Paleo, B. 2016b. {\itshape The Modal Collapse as a Collapse of the Modal Square of Opposition}. Studies in Universal Logic, Springer. pp. 1--7.

@@

\bibitem[{\itshape Rushby(2013)}]{Rushby}
Rushby, J. 2013. {\itshape The Ontological Argument in PVS}. CAV Workshop ``Fun with Formal Methods''. St. Petersburg.

@@

\bibitem[{\itshape Thiele(2003)}]{hilbert} Thiele, R. 2003. {\itshape Hilberts twenty-fourth problem}, American Mathematical Monthly, January.

>>>>

\author{Annika Kanckos \and Bruno Woltzenlogel Paleo}

\authorrunning{A.\~Kanckos \and B.\~Woltzenlogel Paleo}

\institute{ 
 Annika Kanckos \at 
  Department of Philosophy \\
  University of Helsinki\\
  P.O. Box 24 (Unioninkatu 40 A) \\
  Finland \\ 
  \email{annika.siders@helsinki.fi} \\
  +358 2941 29241[2em]
  \and 
  Bruno Woltzenlogel Paleo \at 
  Theory and Logic Group \\ 
  Vienna University of Technology \\ 
  Austria \\
   \email{bruno@logic.at} \\
  \and
    Bruno Woltzenlogel Paleo \at 
  Logic and Computation Group \\
  College of Engineering and Computer Science \\
  Australian National University \\
  Australia
    \email{bruno.woltzenlogel.paleo@anu.edu.au} 
}

@@

%\title{A Variant of G\"{o}del's Ontological Proof \\ in a Natural Deduction Calculus}
%\author{}
%\authorrunning{}
%\institute{}
\maketitle

@@

\bibitem[{\itshape Bentert \& Benzm\"uller \& Streit \& Woltzenlogel Paleo(2016)}]{LeibnizOntologicalProof}
Bentert, M. \& Benzm\"uller, C. \& Streit, D. \& Woltzenlogel Paleo, B. 2016. {\itshape Analysis of an Ontological Proof Proposed by Leibniz}. [to appear in]  Death and Anti-Death, Volume 14: Four Decades after Michael Polanyi, Three Centuries after G. W. Leibniz. Ed. Tandy, C. Ria University Press.

@@

\bibitem[{\itshape Benzm\"uller \& Weber \& Woltzenlogel Paleo(2015)}]{WorldCongressLogicAndReligion}
Benzm\"uller, C. \& Weber, L. \& Woltzenlogel Paleo, B. 2015. {\itshape Computer-Assisted Analysis of the Anderson-Hajek Ontological Controversy}. Handbook of the 1st World Congress on Logic and Religion. Eds. Silvestre, R. S. \& B\'{e}ziau, J-Y.

@@

\bibitem[{\itshape Benzm\"uller \& Woltzenlogel Paleo(2013a)}]{IWIL}
Benzm\"uller, C. \& Woltzenlogel Paleo, B. 2013a. {\itshape G{\"{o}}del's God on the Computer}. Proceedings of the 10th International Workshop on the Implementation of Logics. pp. 1--2.

@@

\bibitem[{\itshape Benzm\"uller \& Woltzenlogel Paleo(2014a)}]{WADT}
Benzm\"uller, C. \& Woltzenlogel Paleo, B. 2014a. {\itshape On Logic Embeddings and G\"odel's God}. Procedings WADT 2014: Revised Selected Papers of the 22nd International Workshop on Algebraic Development Techniques. Eds. Codescu, M. et al. Recent Trends in Algebraic Development Techniques. Springer-Verlag New York. pp. 3--6.

\bibitem[{\itshape Benzm\"uller \& Woltzenlogel Paleo(2014b)}]{WADTPreProceedings}
Benzm\"uller, C. \& Woltzenlogel Paleo, B. 2014b. {\itshape On Logic Embeddings and G\"odel's God}. Preliminary Proceedings of the 22nd International Workshop on Algebraic Development Techniques. Eds. Diaconescu, R. et al. pp. 8--9.

\bibitem[{\itshape Benzm\"uller \& Woltzenlogel Paleo(2014c)}]{SquareOfOpposition}
Benzm\"uller, C. \& Woltzenlogel Paleo, B. 2014c. {\itshape Formalization and Automated Verification of G\"odel's Proof of God's Existence}. Handbook of the World Congress on the Square of Opposition IV. Eds. B\'{e}ziau, J-Y. \& Gan-Krzywoszyrinska, K. pp. 24--25.

\bibitem[{\itshape Benzm\"uller \& Woltzenlogel Paleo(2014d)}]{ECAI2014}
Benzm\"uller, C. \& Woltzenlogel Paleo, B. 2014d. {\itshape Automating G{\"{o}}del's Ontological Proof of God's Existence with Higher-order Automated Theorem Provers}. Proceedings ECAI 2014 - 21st European Conference on Artificial Intelligence- Including Prestigious Applications of Intelligent Systems (PAIS 2014). Eds. Schaub, T. et al. pp. 93--98.

\bibitem[{\itshape Benzm\"uller \& Woltzenlogel Paleo(2015a)}]{CSRModalLogicInCoq}
Benzm\"uller, C. \& Woltzenlogel Paleo, B. 2015a. {\itshape Interacting with Modal Logics in the Coq Proof Assistant}. Computer Science - Theory and Applications - Proceedings of the 10th International Computer Science Symposium in Russia, {CSR} 2015. Lecture Notes in Computer Science. Eds. Beklemishev, L. D. \& Musatov, D. V. Springer. pp. 398--411.

\bibitem[{\itshape Benzm\"uller \& Woltzenlogel Paleo(2015b)}]{ReasoningWebSummerSchool}
Benzm\"uller, C. \& Woltzenlogel Paleo, B. 2015b. {\itshape Higher-Order Modal Logics: Automation and Applications}. Reasoning Web. Web Logic Rules - 11th International Summer School 2015. Tutorial Lectures. Lecture Notes in Computer Science. Springer. pp. 32--74.

\bibitem[{\itshape Benzm\"uller \& Woltzenlogel Paleo(2015c)}]{SpiritualQuest}
Benzm\"uller, C. \& Woltzenlogel Paleo, B. 2015c. {\itshape Experiments in Computational Metaphysics: G\"odel's Proof of God's Existence}. Science and Spiritual Quest: Proceedings of the 9th All India Students' Conference on Science and Spiritual Quest. vol. 9. pp. 23--40.

\bibitem[{\itshape Benzm\"uller \& Woltzenlogel Paleo(2016a)}]{IJCAI2016}
Benzm\"uller, C. \& Woltzenlogel Paleo, B. 2016a. {\itshape The Inconsistency in G\"odel's Ontological Argument: A Success Story for AI in Metaphysics}. Proceedings of the Twenty-Fifth International Joint Conference on Artificial Intelligence - IJCAI. Ed. Kambhampati, S. AAAI Press.

\bibitem[{\itshape Benzm\"uller \& Woltzenlogel Paleo(2016b)}]{ModalCollapse}
Benzm\"uller, C. \& Woltzenlogel Paleo, B. 2016b. {\itshape The Modal Collapse as a Collapse of the Modal Square of Opposition}. Studies in Universal Logic, Ed. B\'{e}ziau, J-Y. Springer. pp. 1--7.

@@

\bibitem[{\itshape Rushby(2013)}]{Rushby}
Rushby, J. 2013. {\itshape The Ontological Argument in PVS}. Proceedings of CAV Workshop ``Fun with Formal Methods''. St. Petersburg. Ed. Shilov, N.

@@

\bibitem[{\itshape Thiele(2003)}]{hilbert} Thiele, R. 2003. {\itshape Hilberts twenty-fourth problem}, American Mathematical Monthly, January 2003.
